\thetitle

### 2021-05-30 writing/challenges.tex
Prettify changelog for sending, and some minor prose changes for it

The {\em second challenge\/} is to find a representative collection of programs
with impedance mismatches.\footnote{\citet{cc-oopsla-20} created a collection of
Reticulated Python programs to evaluate their technique of fixing mistakes in
type annotations. Their collection does not come with type-level mistakes in the
code itself.}  The latter must represent mistakes that programmers accidentally
create and that the run-time checks of academic systems catch. In other words,
the experiment calls for a collection of mistakes in mix-typed programs that is
representative of those ``in the wild.''  Unfortunately no such collection
exists, and with good reason. The kind of mistakes needed are typically detected
by unit or integration tests; even if it takes some time to find their sources,
these mistakes do not make it into code repositories with appropriate commit
messages.

>>>>

The {\em second challenge\/} is to find a representative collection of programs
with impedance mismatches.\footnote{\citet{cc-oopsla-20} created a collection of
Reticulated Python programs to evaluate their technique of fixing mistakes in
type annotations. Their collection does not come with type-level mistakes in the
code itself.}  The impedance mismatches must represent mistakes that programmers accidentally
create and that the run-time checks of academic systems catch. In other words,
the experiment calls for a collection of mistakes in mix-typed programs that is
representative of those ``in the wild.''  Unfortunately no such collection
exists, and with good reason. The kind of mistakes needed are typically detected
by unit or integration tests; even if it takes some time to find their sources,
these mistakes do not make it into code repositories with appropriate commit
messages.

### 2021-05-30 writing/mutate-benchmarks.tex
Prettify changelog for sending, and some minor prose changes for it

Figure~\ref{table:benchmark-descriptions} describes the benchmark programs that
meet all the criteria and come with a sizeable and complex dependency graphs.
This additional filter is needed because Typed Racket demands type assignments
for entire modules. For benchmarks with less than five modules, finding errors
would almost be trivial.

>>>>

Figure~\ref{table:benchmark-descriptions} describes the ten benchmark programs that
meet all the criteria, and furthermore come with the largest dependency graphs.
This additional filter reflects that Typed Racket demands type assignments
for entire modules, and so finding errors in benchmarks with small dependency graphs
would almost be trivial.
